\begin{bibliography}{99}
\addcontentsline{toc}{chapter}{Bibliography}
\begin{enumerate}

	%\bibitem{ref1} 저자 (0000), 제목, \emph{저널}, Vol. 18, No. 3, 543-553.
	
	\bibitem{ref1} Abramson B., Brown J., Edwards W., Murphy A., Winkler R. L. (1996), Hailfinder: A Bayesian system for forecasting severe weather, \emph{International Journal of Forecasting}, Vol. 21, No. 1, 57-71.

	\bibitem{ref1} Beinlich I., Suermondt H. J., Chavez R. M., Cooper G. F. (1989), The ALARM Monitoring System: A Case Study with Two Probabilistic Inference Techniques for Belief Networks, \emph{Proceedings of the 2nd European Conference on Artificial Intelligence in Medicine}, 247-256.
	
	\bibitem{ref1} Benjamin B. Perry (2003), A Genetic Algorithm for Learning Bayesian network adjacency matrices from data, \emph{M.S. thesis, Department of Computing and Information Science College of Engineering, Kansas State University, Manhattan, Kansas}
	
	\bibitem{ref1} Binder J., Koller D., Russell S., Kanazawa K (1997), Adaptive Probabilistic Networks with Hidden Variables, \emph{Machine Learning}, Vol. 29, No. 2-3, 213-244.
	
	\bibitem{ref1} Daly R., Shen Q. (2007), Methods to Accelerate the Learning of Bayesian Network Structures, \emph{Proceedings of the 2007 UK Workshop on Computational Intelligence, Imperial College, London.}
	
	\bibitem{ref1} David Heckerman, Dan Geiger, David M. Chickering (1995), Learning Bayesian Networks: The Combination of Knowledge and Statistical Data, \emph{Machine Learning}, Vol. 20, No. 9, 197-243.
	
	\bibitem{ref1} D.M. Chickering (1996), Learning Bayesian networks is NP-complete, \emph{Learning from Data: Artificial Intelligence and Statistics V, Springer Verlag.}
	
    \bibitem{ref1} Eitel J. M. Lauría (2008), An Information-Geometric Approach to Learning Bayesian Network Topologies from Data, \emph{Innovations in Bayesian Networks Studies in Computational Intelligence}, Vol. 156, 187-217.

	\bibitem{ref1} Fred W. Glover, Manuel Laguna (1997), \emph{TABU Search}, Springer.
		
	\bibitem{ref1} Lauritzen S, Spiegelhalter D (1988), Local Computation with Probabilities on Graphical Structures and their Application to Expert Systems (with discussion), \emph{Journal of the Royal Statistical Society: Series B (Statistical Methodology)}, Vol. 50, No. 2, 157-224.
	
	\bibitem{ref1} Marco Scutari (2010), Learning Bayesian Networks with the bnlearn R Package, \emph{Journal of Statistical Software}, Vol. 35, Issue 3.
	
	\bibitem{ref1} Margaritis D. (2003), Learning Bayesian Network Model Structure from Data, \emph{Ph.D. thesis, School of Computer Science, Carnegie-Mellon University, Pittsburgh, PA}, Available as Technical Report CMU-CS-03-153.

	\bibitem{ref1} Pearl J. (1988), \emph{Probabilistic Reasoning in Intelligent Systems: Networks of Plausible Inference}, Morgan Kaufmann.
	
	\bibitem{ref1} Russell S. J., Norvig P. (2009), \emph{Artificial Intelligence: A Modern Approach}, Prentice Hall, 3rd edition.
	
    \bibitem{ref1} Silvia Acid, Luis M. de Campos, Juan M. Fernandez-Luna, Susana Rodriguez, Jose Maria Rodriguezc, Jose Luis Salcedo (2004), A comparison of learning algorithms for Bayesian networks: a case study based on data from an emergency medical service, \emph{Artificial Intelligence in Medicine}, Vol. 30, 215-232.
	
	\bibitem{ref1} Tsamardinos I, Aliferis CF, Statnikov A (2003), Algorithms for Large Scale Markov Blanket Discovery, \emph{In Proceedings of the Sixteenth International Florida Artificial Intelligence Research Society Conference, AAAI Press.}, 376-381.
	
	\bibitem{ref1} Tsamardinos I., Brown L. E., Aliferis C. F. (2006), The Max-Min Hill-Climbing Bayesian Network Structure Learning Algorithm, \emph{Machine Learning}, Vol. 65, No. 1, 31-78.
	
    \bibitem{ref1} X.-w. Chen, G. Anantha, and X. Wang (2006), An effective structure learning method for constructing gene networks, \emph{Bioinformatics}, Vol. 22, 1367-1374.
\end{enumerate}
\end{bibliography}
