\begin{bibliography}{99}
\addcontentsline{toc}{chapter}{Bibliography}
\begin{enumerate}

	%\bibitem{ref1} 저자 (0000), 제목, \emph{저널}, Vol. 18, No. 3, 543-553.
	
	\bibitem{ref1} Abramson B., Brown J., Edwards W., Murphy A. and Winkler R. L., (1996), Hailfinder: A Bayesian system for forecasting severe weather, \emph{International Journal of Forecasting}, Vol. 21, No. 1, 57-71.
	
	\bibitem{ref1} Alexandra M. C., (2009), Scoring functions for learning Bayesian networks \emph{Inesc-id Tec. Rep.}

	\bibitem{ref1} Beinlich I., Suermondt H. J., Chavez R. M. and Cooper G. F., (1989), The ALARM monitoring system: A case study with two probabilistic inference techniques for belief networks, \emph{Proceedings of the 2nd European Conference on Artificial Intelligence in Medicine}, 247-256.
	
	\bibitem{ref1} Benjamin B. P., (2003), A genetic algorithm for learning Bayesian network adjacency matrices from data, \emph{M.S. thesis, Department of Computing and Information Science College of Engineering, Kansas State University, Manhattan, Kansas}
	
	\bibitem{ref1} Binder J., Koller D., Russell S. and Kanazawa K., (1997), Adaptive probabilistic networks with hidden variables, \emph{Machine Learning}, Vol. 29, No. 2-3, 213-244.
	
	\bibitem{ref1} Daly R. and Shen Q., (2007), Methods to accelerate the learning of Bayesian network structures, \emph{Proceedings of the 2007 UK Workshop on Computational Intelligence, Imperial College, London.}
	
	\bibitem{ref1} D. Heckerman, D. Geiger and D. M. Chickering, (1995), Learning Bayesian networks: The combination of knowledge and statistical data, \emph{Machine Learning}, Vol. 20, No. 9, 197-243.
	
	\bibitem{ref1} D. M. Chickering, (1996), Learning Bayesian networks is NP-complete, \emph{Learning from Data: Artificial Intelligence and Statistics V, Springer Verlag.}
	
    \bibitem{ref1} Eitel J. M. L., (2008), An Information-geometric approach to learning Bayesian network topologies from data, \emph{Innovations in Bayesian Networks Studies in Computational Intelligence}, Vol. 156, 187-217.

	\bibitem{ref1} Fred W. G. and Manuel L., (1997), \emph{TABU Search}, Springer.

	\bibitem{ref1} J. Cheng, R. Greiner, J. Kelly, D. Bell and W. Liu, (2002), Learning Bayesian networks from data: An information-theory based approach, \emph{Artificial Intelligence}, Vol. 137, No. 1-2, 43-90.
	
	\bibitem{ref1} Kevin B. K. and Ann E. N., (2010), \emph{Bayesian Artificial Intelligence, 2nd Edition}, CRC Press.
		
	\bibitem{ref1} Lauritzen S. and Spiegelhalter D., (1988), Local computation with probabilities on graphical structures and their application to expert systems (with discussion), \emph{Journal of the Royal Statistical Society: Series B (Statistical Methodology)}, Vol. 50, No. 2, 157-224.
	
	\bibitem{ref1} Marco S., (2010), Learning Bayesian networks with the bnlearn R package, \emph{Journal of Statistical Software}, Vol. 35, Issue 3.
	
	\bibitem{ref1} Margaritis D., (2003), Learning Bayesian network model structure from data, \emph{Ph.D. thesis, School of Computer Science, Carnegie-Mellon University, Pittsburgh, PA}, Available as Technical Report CMU-CS-03-153.
	
	\bibitem{ref1} Margaritis D. and Thrun S., (1999) Bayesian network induction via local neighborhoods, \emph{Proceedings of Conference on Neural Information Processing Systems (NIPS-12)}, MIT Press.

	\bibitem{ref1} Pearl J., (1988), \emph{Probabilistic Reasoning in Intelligent Systems: Networks of Plausible Inference}, Morgan Kaufmann.
	
	\bibitem{ref1} R. Daly and Q. Shen., (2007), Methods to accelerate the learning of Bayesian network structures.  \emph{Proceedings of the Proceedings of the 2007 UK Workshop on Computational Intelligence.} 
	
	\bibitem{ref1} Russell S. J. and Norvig P., (2009), \emph{Artificial Intelligence: A Modern Approach}, Prentice Hall, 3rd edition.
	
    \bibitem{ref1} Silvia A., L. M. de Campos, Juan M. F., Susana R., Jose M. and Jose L. S., (2004), A comparison of learning algorithms for Bayesian networks: a case study based on data from an emergency medical service, \emph{Artificial Intelligence in Medicine}, Vol. 30, 215-232.
	
	\bibitem{ref1} Tsamardinos I., Aliferis C. F. and Statnikov A., (2003), Algorithms for large scale Markov blanket discovery, \emph{In Proceedings of the Sixteenth International Florida Artificial Intelligence Research Society Conference, AAAI Press.}, 376-381.
	
	\bibitem{ref1} Tsamardinos I., Brown L. E. and Aliferis C. F., (2006), The Max-Min hill-climbing Bayesian network structure learning algorithm, \emph{Machine Learning}, Vol. 65, No. 1, 31-78.
	
    \bibitem{ref1} X.-w. Chen, G. Anantha, and X. Wang, (2006), An effective structure learning method for constructing gene networks, \emph{Bioinformatics}, Vol. 22, 1367-1374.
\end{enumerate}
\end{bibliography}
